% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{xfrac}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Matthew B. O'Connor}}

4004 Mallow Road\ \ \textbullet
\ \ Colorado Springs, CO 80907
\\
719 337 8776\ \ \textbullet
\ \ thegreendragon@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{DirectStream, LLC (formerly SRC Computers, LLC)}}
		{\textbf{Colorado Springs, CO}}
	\\
	\headerrow
		{\emph{Senior Software Engineer}}
		{\emph{2013 -- present}}
	\begin{description}
		\item[2013 -- present] \hfill \\
				Writing a \CPP \  compiler using LLVM/Clang that produces Verilog for execution on an FPGA. \\
				Implementing optimizations on the internal dataflow graph. \\
				Crafting a threading system to enable parallel use of the FPGA’s resources. \\
	\end{description}

	\item
	\headerrow
		{\textbf{Intelligent Software Solutions, Inc.}}
		{\textbf{Colorado Springs, CO}}
	\\
	\headerrow
		{\emph{Software Engineer}}
		{\emph{2006 -- 2013}}
	\begin{description}
		\item[2012 -- 2013] \hfill \\
				Worked on the data processing side of a 3-tier web-based analytics engine. \\
				Designed an API using Java annotations and backed by reflection to simplify developer use.
		\item[2010 -- 2012] \hfill \\
				Developed a data processing application that produced \& processed hundreds of gigabytes of in-memory data that it exposed via web services. \\
				Fixed threading \& performance issues, improving runtimes from overnight to a few minutes.
		\item[2008 --2010] \hfill \\
				Worked at a customer’s site, interacting daily, to expose legacy programs via web services \& UI. \\
				Helped determine requirements, priorities, \& handle emergencies. \\
				Responsible for the UI and coordinating with the web services developer to ensure service support.
		\item[2007 -- 2008] \hfill \\
				Extended the previous project with additional external databases. \\
				Wrote the mappings between the external databases and the internal data format.
		\item[2006 -- 2007] \hfill \\
				Hired for a project that managed \& integrated external databases \& provided a UI to allow analysis, management, planning, \& visualization. \\
				Mastered and accepted responsibility for modifying the program’s data model.
	\end{description}

	\item
	\headerrow
		{\textbf{Zero}}
		{\textbf{https://github.com/oconnor0/zero}}
	\\
	\headerrow
		{\emph{Designer and Sole Engineer}}
		{\emph{2012}}
	\begin{itemize}
		\item Started developing a programming language targeting the JVM.
		\item Wrote parser and AST-walking interpreter.
		\item Can write and correctly evalute Fibonacci.
	\end{itemize}

	\item
	\headerrow
		{\textbf{New Life Church}}
		{\textbf{Colorado Springs, CO}}
	\\
	\headerrow
		{\emph{Software Engineer}}
		{\emph{September -- October 2005}}
	\begin{itemize}
		\item Modified an existing open source ticketing system to meet needs.
		\item Deployed to production and used to sell thousands of tickets for multiple shows for Christmas and Easter events.
	\end{itemize}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{University of Colorado, Colorado Springs}}
		{\textbf{Colorado Springs, CO}}
	\\
	\headerrow
		{\emph{College of Engineering and Applied Science, B.S. in Computer Science}}
		{\emph{2002 -- 2005}}
	\begin{description}
		\item[Coursework] Compilers, operating systems, computer architecture, automata, algorithms, data structures, numerical computing, assembler, Unix, C, Java, object-oriented programming and design, and web programming.
	\end{description}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Skills and Interests}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description}
	\item[Languages:] \ \\
	Experience in \CPP \ , Java, \LaTeX, and Verilog. \\
	Written in Bash, C, Clojure, Coq, elisp, Haskell, Javascript, \LaTeX, Lua, Mozart/Oz, OCaml, Rust, SQL.
	\item[Tooling:] \ \\
	Altera Quartus, Ant, CVS, Git, Icarus Verilog, Make, Maven, SVN.
	\item[Interests:] \ \\
	Programming languages, compiler design, type systems, type theory, performance, high-level languages, programs-as-proofs, game development.
\end{description}
\end{indentsection}

\end{document}
